\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Pushpender Sharma} % Your name
% You can merge both of these into a single line if you do not have a website.
\address{+91 9672249796 \\ pushpendersharma2019@gmail.com \\ Delhi, India} 
\address{\href{mailto:pushpendersharma2019@gmail.com}{Gmail} \\ \href{https://www.linkedin.com/in/pushpendersharma/}{LinkedIn} \\ 
\href{https://github.com/ipushpie/}{GitHub} \\ 
\href{https://pushpender-portfolio.web.app/}{PortFolio}} 

\begin{document}
%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
\begin{rSection}{OBJECTIVE}
{Software Engineer with 3 years of experience in full-stack development and AI-driven solutions, building enterprise-grade applications, microservices, and LLM-powered automation. Skilled at architecting scalable, high-performance systems, leading development teams, and delivering production-ready solutions with measurable business impact.
}


\end{rSection}
%----------------------------------------------------------------------------------------

% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & JavaScript, TypeScript, Python, C++, Go, HTML/CSS \\
Frameworks & React.js, Next.js, Angular, Node.js, Express.js, NestJS, FastAPI \\
Libraries & Redux, Zustand, Axios, Tanstack, Tailwind, Bootstrap, Chart.js, Recharts, MUI, Shadcn  \\
Databases & PostgreSQL (with PGVector), MySQL, SQLite,MongoDB  \\
Tools & Git, Docker, REST APIs, NPM, PNPM, UV, PIP, Nginx, Caddy\\
Cloud & Firebase, Vercel, Netlify, Hostinger, Heroku, Render, Railway\\
Concepts & Data Structures and Algorithms (DSA), System Design, Data Analytics, RAG \\
Soft Skills & Teamwork, Problem-solving, Leadership, Communication, Time Management \\
\end{tabular}


\end{rSection}

\begin{rSection}{EXPERIENCE}


\textbf{Senior Software Engineer} \hfill Nov 2024 - Present\\
GoTrust / AppVin (Sister Company) \hfill \textit{Noida, UP}
 \begin{itemize}
    \itemsep -6pt {}
        
     \item Heavily contributed to the development of \href{https://www.gotrust.tech/}{GoTrust}, a privacy-autonomous tool built to comply with India’s Digital Personal Data Protection Act (DPDPA) and other privacy laws, implementing core architectural components such as interceptors, routing, theming, state management, and database schema design, while integrating AI-driven guidance and interactive assistants to enhance usability.

     \item Architected and led an AI-powered automation microservice   within \textbf{GoTrust}, leveraging a localized LLM via \textbf{Ollama} to orchestrate interactions across multiple internal services, delivering production-grade automation and significantly improving system efficiency.

     \item Contributed to \textbf{DLP Pro}, an enterprise-grade Data Loss Prevention system, developing multi-platform agents (Windows, macOS, Linux, browser) and high-performance backend services, enabling sub-10ms event processing, real-time policy enforcement, and secure handling of sensitive data across thousands of endpoints.

     \item Dockerized the system, cutting customer deployment/setup time by 80\% and reducing configuration errors by 40\%, significantly enhancing portability, adoption, and operational reliability.


     \item Developed \href{https://m-ait.com/}{MAIT} for \href{https://multistrat.net/}{MultiStrat}, an AI-agentic application that automated contract analysis using retrieval-augmented techniques on vector databases and Gemini APIs, reducing manual review effort by 60\% and delivering significantly faster, data-backed insights for clients. 

    \item Led the development of an AI-powered due diligence platform for \href{https://sidebarlaw.in/}{SidebarLaw}, enabling autonomous review of contracts, agreements, and financial documents — projected to cut analysis costs by 50\% while improving accuracy and compliance. 

    \item Mentored the development team for \href{https://verdex.co.in/}{VerdeX}, a full-stack B2B carbon credit trading platform, guiding implementation of RBAC, marketplace features, blockchain integration , audit trails, dispute management, and containerized deployment with Docker.
 
    \end{itemize}

\textbf{Software  Engineer} \hfill Jan 2023 - Nov 2024\\
RemoteState \hfill \textit{Noida, UP}
 \begin{itemize}
 \itemsep -5pt {} 
   \item Served as the tech lead for the project \href{https://precium.in}{Precium}, where I played a key role in developing impactful new features using React.js. These enhancements significantly boosted user engagement and led to a 30\% increase in new clients, strengthening the platform's market presence.


     \item Spearheaded efforts to enhance the \href{https://www.circonomy.co/}{Circonomy} website built with Next.js, resulting in a substantial increase of 60\% in visitor traffic and engagement.
     \item Played a pivotal role in delivering the app \href{https://ux.com.au}{ux.com.au} on time, ensuring adherence to project deadlines.
     \item Contributed to the development and success of the application \href{https://educationplanner.io}{Education Planner}, incorporating user feedback to optimize usability and functionality.
     \item Developed a comprehensive backend-driven application using React.js for \href{https://nvest.in/}{Nvest}, where the architecture is designed to ensure that all functionalities are controlled from the backend, enhancing security and efficiency.
 \end{itemize}


\textbf{Web Development Intern} \hfill June 2022 - Dec 2022\\
Bennett University \hfill \textit{Greater Noida, UP}
 \begin{itemize}
 \itemsep -5pt {} 
   \item Implemented substantial enhancements to the university website to boost visitor engagement and traffic.  
   \item Developed a dedicated website for the university's cultural festival, showcasing events and activities.

  \end{itemize}

    
\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{PROJECTS}
% \vspace{-1.25em}
% \item \textbf{SocioPedia:} Developed a social media platform using the MERN stack (MongoDB, Express.js, React.js, Node.js) with features such as posts, comments, and authentication. Onboarded a class of 30+ students during testing, gathering feedback that guided iterative improvements through Agile practices. \hfill \href{https://github.com/ipushpie/SocioPedia}{GitHub}


% \item \textbf{Eat4Fun:} Developed a food delivery application using JavaScript and TypeScript with React.js (frontend), Express.js (backend), and MySQL (database). Designed a responsive interface with Bootstrap and integrated the app with the college canteen, successfully attracting 140+ hostel students as active users. \hfill \href{https://github.com/ipushpie/Eat4Fun}{GitHub}

% \item \textbf{Wikipedia Search Engine:} Built a search engine for Wikipedia using Python and PySpark with Natural Language Processing (NLP) techniques. Processed 200+ Wikipedia articles and delivered query results within 2–3 seconds on a college lab setup. Completed during a 24-hour Datacouch Big Data Analytics hackathon, showcasing the ability to design and implement an end-to-end search pipeline with Hadoop tools under time constraints. \hfill
% \href{https://github.com/ipushpie/Wikipedia-Search-Engine}{GitHub}

% \end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}
    \item	Secured a Design Patent and TM ownership for a women's safety gadget (Ring), developed during a semester project, encompassing its design and idea.
    \item	Successfully advanced through the first round of the SIH National Hackathon, showcasing expertise and clearing the college round amidst stiff competition.
    \item	Acted as the Captain of the Blue house at school, orchestrating various house events and activities throughout the academic year.
\end{itemize}


\end{rSection}

%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Science}, Bennett University \hfill {2020 - 2024}\\
9.0 CGPA with an academic scholarship.

{\bf 12th  Grade}, Raath International School \hfill {2019}\\
Scored 94\% and won many quizzes and certificates.
% Scored 94\% in boards
%Minor in Linguistics \smallskip \\
% Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% \end{itemize}


% \end{rSection}


\end{document}
